---
title: "Assignment 3"
output: html_notebook
---


Import the College Dataset.

```{r}
fileURL <- "https://ed-public-download.apps.cloud.gov/downloads/Most-Recent-Cohorts-Scorecard-Elements.csv"
download.file(fileURL,destfile = "CollegeData.csv",method = "auto")
list.files(".")
CS <- read.csv("CollegeData.csv",na.strings = c("NULL","PrivacySuppressed"))
head(CS)
```

Before we demonstrate decision trees, we have to install the 
requisite packages.

```{r}
pkgs <- c("rpart", "rpart.plot", "party")
install.packages(pkgs)
```

Replace the values of 0 and 0.0000 to NA

```{r}
CS [CS == 0] <- NA
CS[CS==0.0000] <- NA
```

Delect the columns with over 70% percentage of value missing

```{r}
CS1 <- CS[,-which(colMeans(is.na(CS))>0.3)]
```


The object is to predict the median debt, which is attribute 'GRAD_DEBT_MDN_SUPP'.
We have to set trainning set before doing analysis.

```{r}
set.seed(1234)
train <- sample(nrow(CS1), 0.7*nrow(CS1))
CS1.train <- CS1[train,]
CS1.validate <- CS1[-train,]
dim(CS1.train)
dim(CS1.validate)
```


Fit the tree
```{r}
library(rpart)
Dtree <- rpart(GRAD_DEBT_MDN_SUPP~.,data=CS1.train,method="anova",parms=list(split="information"))
Dtree$cptable
```

Select the smallest cross-validation error
```{r}
plotcp(Dtree)
PV <- Dtree$catable[which.min(Dtree$captable[,"xerror"]),"CP"]
Dtree.p <- prune(Dtree,cp=PV)
Dtree.p
plotcp(Dtree.p)
Dtree.p$captable
```

Plot the tree

```{r}
library(rpart.plot)
prp(Dtree.p,type=2,extra=100,fallen.leaves = T,main="Decision Tree")
```

Decision tree on validation set

```{r}
Dtree.pred <- predict(Dtree.p,CS1.validate)
summary(Dtree.pred)
Dtree.pred
```

